{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-02-11 thesis/landslide.tex
fix some stuff

Despite being algorithmically worse in the size of the vector clocks,
I use the {\sc Djit+} rules for reads and writes rather than the {\tt FastTrack} ones;
because Landslide tests should be limited to few threads to manage the state space size,
$O(n)$ is usually in the single digits, so I optimize for code simplicity.

\begin{itemize}
	\item Reads and Writes (writes vs reads comparison already handled by DPOR) ({\tt memory.c})
	\begin{itemize}
		\item \textsc{Djit+ read/write same epoch} - {\tt vc\_eq()} case of {\tt add\_lockset\_to\_shm()}
		\item \textsc{Djit+ read/write} - {\tt vc\_happens\_before()} case of {\tt check\_locksets()}
	\end{itemize}
	\item Synchronization ({\tt schedule.c})
	\begin{itemize}
		\item \textsc{FT acquire}
			\begin{itemize}
				\item {\tt kern\_mutex\_\{,try\}locking\_done()} cases of {kern\_update\_state\_machine()}
				\item {\tt user\_mutex\_\{,try\}lock\_exiting()} cases of {user\_update\_state\_machine()}
				\item {\tt cli} case of {\tt kern\_update\_state\_machine()} (Pintos only)
				\item {\tt cli}/{\tt sti} lock handoff case in {\tt sched\_update()} (Pebbles only)
			\end{itemize}
		\item \textsc{FT release}
			\begin{itemize}
				\item {\tt kern\_mutex\_unlocking()} case of {kern\_update\_state\_machine()}
				\item {\tt user\_mutex\_unlock\_entering()} case of {user\_update\_state\_machine()}
				\item {\tt sti} case of {\tt kern\_update\_state\_machine()} (Pintos only)
				\item {\tt cli}/{\tt sti} lock handoff case in {\tt sched\_update()} (Pebbles only)
			\end{itemize}
		\item \textsc{FT fork} - {\tt agent\_fork()}
		\item \textsc{FT join} - {\tt sched\_unblock()} case of {\tt kern\_update\_state\_machine()} (Pebbles only)
	\end{itemize}
\end{itemize}

>>>>

I use the {\sc Djit+} rules for reads and writes rather than the {\tt FastTrack} ones,
even though they incur $O(n)$ runtime in the size of the vector clocks more often:
because Landslide tests should be limited to few threads to manage the state space size,
$O(n)$ is usually in the single digits, so I optimize for code simplicity.

\begin{itemize}
	\item Reads and Writes ({\tt memory.c})
	\begin{itemize}
		\item \textsc{Djit+ read/write same epoch} - {\tt vc\_eq()} case of {\tt add\_lockset\_to\_shm()}
		\item \textsc{Djit+ read/write} - {\tt vc\_happens\_before()} case of {\tt check\_locksets()}
	\end{itemize}
	\item Synchronization ({\tt schedule.c})
	\begin{itemize}
		\item \textsc{FT acquire}
			\begin{itemize}
				\item {\tt kern\_mutex\_\{,try\}locking\_done()} cases of {\tt kern\_update\_state\_\allowbreak{}machine()}
				\item {\tt user\_mutex\_\{,try\}lock\_exiting()} cases of {\tt user\_update\_state\_\allowbreak{}machine()}
				\item {\tt cli} case of {\tt kern\_update\_state\_machine()} (Pintos only)
				\item {\tt cli}/{\tt sti} lock handoff case in {\tt sched\_update()} (Pebbles only)
			\end{itemize}
		\item \textsc{FT release}
			\begin{itemize}
				\item {\tt kern\_mutex\_unlocking()} case of {\tt kern\_update\_state\_machine()}
				\item {\tt user\_mutex\_unlock\_entering()} case of {\tt user\_update\_state\_machine()}
				\item {\tt sti} case of {\tt kern\_update\_state\_machine()} (Pintos only)
				\item {\tt cli}/{\tt sti} lock handoff case in {\tt sched\_update()} (Pebbles only)
			\end{itemize}
		\item \textsc{FT fork} - {\tt agent\_fork()}
		\item \textsc{FT join} - {\tt sched\_unblock()} case of {\tt kern\_update\_state\_machine()} (Pebbles only)
	\end{itemize}
\end{itemize}
